---
title: "Truth leakage, declaration and repair"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Truth leakage, declaration and repair}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The leaky callback closes over the protected truth vector. Declaring dependence requires human review. The repaired callback receives only accessible inputs; the protected assignment never enters its construction. The supported outcome follows an explicit synthetic author rule, not an automatic biological conclusion.

```{r setup, include=FALSE}
library(MeasureQual)
source(system.file("examples", "toy-workflow.R", package = "MeasureQual"))
```

The complete synthetic declaration is installed at
`system.file("examples", "toy-workflow.R", package = "MeasureQual")`.
Its scientific choices are illustrative declarations, never engine defaults.

```{r}
leaky <- toy_spec(leak = TRUE)
blocked <- check_audit(freeze_audit(leaky$spec), leaky$data)
stopifnot(blocked$integrity$outcome == "INVALID_TRUTH_LEAKAGE")
declared <- toy_spec(truth_dependence = TRUE)
c <- check_audit(freeze_audit(declared$spec), declared$data)
stopifnot("DECLARED_TRUTH_DEPENDENCE" %in% c$flags)
repaired <- toy_spec("SUPPORTED_WITHIN_DOMAIN")
s <- amend_audit(repaired$spec, "SCIENTIFIC", "Declare bounded scope", "example analyst",
 list(flags = c("PANEL_BOUNDED", "DOMAIN_BOUNDED", "LOW_SCIENTIFIC_N")))
c <- check_audit(freeze_audit(s), repaired$data)
stopifnot(c$integrity$outcome == "PASS_PROBED")
r <- evidence_record(run_audit(c, repaired$data), render = FALSE)
stopifnot(r$qualification$terminal_state == "SUPPORTED_WITHIN_DOMAIN")
r$interpretation_license$required_qualifiers
r$interpretation_license$prohibited_extensions
```

The package does not rank signatures, infer biological truth, or transfer a licence between contexts.
