---
title: "Constructibility and inferential support"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Constructibility and inferential support}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A zero-capacity cell blocks execution. A separate design whose smallest attainable probability is 1/16 cannot reach an explicitly declared alpha of .05. Later gates remain unassessed after the first block.

```{r setup, include=FALSE}
library(MeasureQual)
source(system.file("examples", "toy-workflow.R", package = "MeasureQual"))
```

The complete synthetic declaration is installed at
`system.file("examples", "toy-workflow.R", package = "MeasureQual")`.
Its scientific choices are illustrative declarations, never engine defaults.

```{r}
for (t in list(toy_spec(capacity = FALSE), toy_spec(min_p = 1/16))) {
  check <- check_audit(freeze_audit(t$spec), t$data)
  stopifnot(check$entry_gate == "BLOCKED")
  r <- evidence_record(check, render = FALSE)
  stopifnot(r$qualification$terminal_state == "NOT_EVALUABLE")
  print(r$interpretation_license$suppression)
}
```
